Modelling the emergence of whisker barrels

### 2020-06-02 paper/briefpaper/brief.tex
6*6*6 is not 180!

\cmnt{To determine the robustness of the model to its parameters, we
  investigated its behaviour with respect to changes in the parameters $D$,
  $\epsilon$ and the ratio of $\alpha$ to $\beta$. Fig.\,\ref{fig:paramsweep}A
  shows the value of the metrics $\delta$, $\eta$ and $\omega$ after $30000$
  iterations plotted as colour maps for $180$ parameter sets. Each row of maps
  shows the results for a separate metric. Each column of maps shows
  results for a different value of the ratio $\alpha / \beta$. The diffusion
  parameter, $D$ varies with the $x$ axes and the strength of competition,
  $\epsilon$ varies with the $y$ axes. The colour maps are arranged so that
  `yellow is good'. Lower values of $\delta$ indicate good Voroni patterns and
  are yellow. Lower values of the difference between real and simulated barrel
  area indicates good pattern matching. Higher values of $\omega$ indicate
  better localization and are coloured yellow. White squares indicate that the
  simulation was not stable for that parameter set.}

>>>>

\cmnt{To determine the robustness of the model to its parameters, we
  investigated its behaviour with respect to changes in the parameters $D$,
  $\epsilon$ and the ratio of $\alpha$ to $\beta$. Fig.\,\ref{fig:paramsweep}A
  shows the value of the metrics $\delta$, $\eta$ and $\omega$ after $30000$
  iterations plotted as colour maps for $216$ parameter sets. Each row of maps
  shows the results for a separate metric. Each column of maps shows
  results for a different value of the ratio $\alpha / \beta$. The diffusion
  parameter, $D$ varies with the $x$ axes and the strength of competition,
  $\epsilon$ varies with the $y$ axes. The colour maps are arranged so that
  `yellow is good'. Lower values of $\delta$ indicate good Voroni patterns and
  are yellow. Lower values of the difference between real and simulated barrel
  area indicates good pattern matching. Higher values of $\omega$ indicate
  better localization and are coloured yellow. White squares indicate that the
  simulation was not stable for that parameter set.}
